An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-06-30 casestudy.tex
case study equations (needs to be done by hand)
Updated related work
produced even more obvious formulation
Added gist of the argument for case study

Claudio writes this section

>>>>

In this section, we give a simple example of a co-simulation whose correct initialization demands the solution to an algebraic loop.

In the example case study, the acceleration can be set to 0, at time 0.
We show that \verb|tire_x| depends on itself as a consequence:
\begin{verbatim}
0 = a = (1/tire_mass) * F_total
0 = F_total = F_rubber + F_suspension - f_gravity
f_gravity - F_suspension = F_rubber
F_rubber = - rubber_stiffness*tire_x - rubber_damping * tire_v
tire_v = 0
F_rubber = - rubber_stiffness*tire_x

F_suspension = suspension_stiffness*(car_x - tire_x) + suspension_damping*(car_v - tire_v);

tire_x = F(F_rubber) = G(F_suspension)= H(tire_x)
\end{verbatim}
